Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-24 Manuscript/manuscript.tex
nearly finished revisions

\begin{figure*}
\centering
\includegraphics[width=10cm]{../Scripts/scratch/cor_comparison.pdf}
\caption{The between- and within-task correlations for the three different search tasks. The bars indicate the $95\%$ confidence intervals for Pearson's correlation coefficient. Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}). Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy.}
\label{fig:all_the_cor}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=10cm]{../Scripts/scratch/cor_comparison.pdf}
\caption{The between- and within-task correlations for the three different search tasks. The bars indicate the $95\%$ confidence intervals for Pearson's correlation coefficient. Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}). Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy. \textcolor{blue}{The \textit{opt} measures reflect the extent to which participants adhered to an optimal strategy.}}
\label{fig:all_the_cor}
\end{figure*}
